


```{r}
#import dataset
df <- read.csv(here("data_", "lyrics_runs.csv"))
test_df <- df %>% filter(personality=="True"|topic=="True"|linguistic=="True"|liwc=="True"|value=="True"|audio=="True")
```

This dataset is the result of a series of runs of various system setups on three MIR tasks. The response variable, "score", is the output of each run where a higher score was more successful. The "task" column is a nominal variable representing each of the three tasks: genre classification, autotagging, or recommender system. Three systems were used for each task, and are in the "models" column as a nominal variable. 

The columns "personality", "liwc", "topic", "value", "linguistic" and "audio" represent the feature sets used in The values in these columns are either "True" or "False" depending on whether or not they were used in a given trial run. There were 5 trials run for each configuration. 

```{r}
head(df)
```

```{r}
#convert "True" and "False" to 1 and 0 respectively, for analysis
TrueFalseToNumbers <- function(x, print=TRUE){
  x <- as.character(x)
  x <- replace(x, x=="True", "1")
  x <- replace(x, x=="False", "0")
  x <- as.numeric(x)
  return(x)
}

test_df$personality <- TrueFalseToNumbers(test_df$personality)
test_df$liwc <- TrueFalseToNumbers(test_df$liwc)
test_df$topic <- TrueFalseToNumbers(test_df$topic)
test_df$value <- TrueFalseToNumbers(test_df$value)
test_df$linguistic <- TrueFalseToNumbers(test_df$linguistic)
test_df$audio <- TrueFalseToNumbers(test_df$audio)

```

We add two columns for exploratory analysis, one representing the number of feature sets used in each run, and a second representing the overall number of features used in each run. 

```{r}
test_df$feature_number <- (test_df$personality+test_df$topic+test_df$linguistic+test_df$liwc+test_df$value+test_df$audio)

test_df$dimension_number <- (test_df$personality*5+test_df$topic*25+test_df$linguistic*9+test_df$liwc*72+test_df$value*49+test_df$audio*240)


```

```{r, results=FALSE}
#convert variables to factors
lapply(test_df[,c('personality', 'topic', 'value', 'audio', 'linguistic', 'liwc')], as.factor)
```


