Given the structure of the data, we can plausibly estimate interactions of all combinations of fixed effects and task. Specifically, our feature sets are all represented as binary variables. For example, a four-way interaction represents the effect of all four variables being included. However, this is estimating a large number of terms that, if all included, would hamper interpretability. 

Included in the lmerTest package (Kuznetsova et al.) is a step function. This function removes one term at a time, and tests the difference between models if it is left out:
https://www.jstatsoft.org/index.php/jss/article/view/v082i13/v82i13.pdf

The stepping procedure only looked at the fixed effects; as such, the fixed effect structure would be the same for all random effect structures, of a response variable treatment. 

#reduction of fixed effects for standardized score
The iterative reduction of fixed effects found the following forumula:
score_z ~ liwc + value + task + audio + liwc:task + value:task
```{r, results=FALSE}
load(here("models", "m8.1.rda"))
f0.1 <- lm(formula(m8.1,fixed.only=TRUE), data=eval(getCall(m8.1)$data))
step(f0.1)
```

#reduction of fixed effects for logit score
The iterative reduction of fixed effects found the following forumula:
score_log ~ liwc + value + task + audio + liwc:value + liwc:task + value:task + liwc:value:task
    
```{r, results=FALSE}
load(here("models", "l8.4.rda"))
f1.1 <- lm(formula(l8.4,fixed.only=TRUE), data=eval(getCall(l8.4)$data))
step(f1.1)
```

#reduction of fixed effects for raw score
The iterative reduction of fixed effects found the following forumula:
score ~ liwc + task + audio + liwc:task

```{r, results=FALSE}
load(here("models", "r0.1.rda"))
f2.1 <- lm(formula(r0.1,fixed.only=TRUE), data=eval(getCall(r0.1)$data))
step(f2.1)
```

